---
title: "README"
output: html_document
---
# Short Intro
Hello there!
This is a project for the Course Getting and Cleaning Data.
I tried to explain all steps in the code, here I provide simple codebook for all variables. As you can see from the names of the variables, I do not know all technical details very well, but I tried my best.

I am not native English speaker, so if you have recommendation how to effectively and fast learn English , I will very happy.

Any feedback (especially negative) is highly appreciated.

# How the data was produced
## Mining
First I write he function to extract data from folders. They differ only in name (test and train). What function do: it takes folder names, construct path with files name and read it to data frames. Result: we obtain two lists of data (train and test). I cannot transform them to dataframes, because almost all variables have different length.

## Join and subset the data
I use mapply function to bind variables from train and test data. 
I load labels from txt files and add them to list.
I subset the data, using regular expressions. It helps to preserve only rows with mean and standard deviation.

## Transform the data
I split the names to obtain the column with 'mean-sd' variable and then collect the names again. This variable helps to reshape data into tidy format.

# Codebook

Note, that sygnal is measured in three directions (for example, body acceleration signal (frequency domain signal) in X direction is coded as 'fBodyAcc X'). Magnitudes have no direction.

```{r, echo=FALSE, results='hide'}    
dt.temp <- read.csv('1.csv')
output <- cbind(as.character(unique(dt.temp$X1)),  
      c(
        'Gravity acceleration signals (time domain signal)',
        'Gravity sygnal (time domain signal)',
        'Body acceleration signal (time domain signal)',
        'Body Jerk signal (frequency domain signal)',
        'Body Jerk signal (time domain signal)',
        'Magnitude of body acceleration signal (time domain signal)',
        'Magnitude of body Jerk signal (frequency domain signal)',
        'Body acceleration signal (frequency domain signal)',
        'Magnitude of body (twice) gravity Jerk signal (frequency domain signal)',
        'Body gravity sygnal (time domain signal)',
        'Magnitude of body acceleration Jerk signal (time domain signal)',
        'Magnitude of body gravity Jerk signal (time domain signal)',
        'Magnitude of body (twice) gravity Jerk signal (frequency domain signal)',
        'Magnitude of gravity acceleration signals (frequency domain signal)',
        'Magnitude of gravity acceleration signals (time domain signal)',
        'Magnitude of body (twice) Jerk signal (time domain signal)',
        'Magnitude of body gravity signal ((time domain signal)'
        ))
colnames(output) <- c('Variable', 'Description')

```
```{r}, echo=FALSE, warning=FALSE}
library(knitr)
 kable(output, format = "markdown") 

```

                   